\LaTeXe\ guide for the Journal of Functional Programming

### 2019-04-28 papers/jfp/5-rebuilders.tex
Explain post-build keys

\q{Andrey}{The "function for obtaining the post-build value of any key" is a bit
mysterious. It would be nice to add a clarification. Or could we simplify the
interface and only provide a function with type
\hs{k -> Hash v -> [(k, Hash v)] -> VT k v -> Bool}? Presumably, \hs{verifyVT}
with the current type signature could be built on top of it?}

>>>>

The most complex argument of \hs{verifyVT} is a function to obtain the post-build
value of any key, which we refer to as \hs{fetch}. With an \hs{Applicative} task,
\hs{fetch} will be called on the dependencies of the \hs{k} argument. However, with a
\hs{Monad} task, the dependencies are not known from the task alone, they are only
recorded from previous executions and stored in \hs{VT}. If the build system has
two traces for a given \hs{k}, they will both request the same dependency first,
since \hs{Task} is determinstic. However, depending on that first result,
they may then request different successive dependencies from \hs{fetch}. A curious
result is that for suspending schedulers (\S\ref{sec-suspending}) in many cases
the actual build steps are performed as a consequence of checking if a key needs rebuilding!
